---
title: "Final Exam"
author: "Echo Nattinger (en6235)"
date: "7/8/2021"
output: word_document
---
GITHUB REPO LINK: <https://github.com/enatt/Exam3>

```{r setup, message=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

```{r}
rm(list=ls(all=TRUE))
```

```{r}
# Loading and preparing data
library(WDI)
library(tidyverse)
female_lfp = WDI(country="all",
                 indicator="SL.TLF.CACT.FE.ZS", 
                 start=2010, end=2015, 
                 extra=FALSE, cache=NULL)

female_lfp = female_lfp%>%
  rename(flfp = SL.TLF.CACT.FE.ZS)

flfp_no_NAs = na.omit(female_lfp, select=c("flp"))
# Collapsing data
collapsed_flfp = flfp_no_NAs%>%
  group_by(country)%>%
  summarize(average = mean(flfp),
            iso2c = iso2c)

# Which countries have average participation rates less than 15%
q5 = collapsed_flfp %>%
  filter(average < 15)
q5
```


```{r, message=TRUE}
# Libraries
library(sp)
library(sf)
library(geosphere)
library(devtools)
library(rnaturalearthhires)
library(ggsflabel)
library(mapdata)
library(rio)
library(tidyverse)
library(labelled)
library(data.table)
library(googlesheets4)
library(varhandle)
library(ggrepel)
library(rgeos)
library(viridis)
library(mapview)
library(rnaturalearth)
library(rnaturalearthdata)
library(remotes)
library(raster)
library(Imap)

# Loading map
# Adding border data to female participation rate data
world_borders = st_read("World_Borders.shp", stringsAsFactors=FALSE)
borders = st_transform(world_borders, "+proj=longlat +ellps=WGS84 +datum=WGS84")
rm(world_borders)

# Changing the name of borders to make merging easier
setnames(borders, "NAME", "country")
setnames(borders, "ISO2", "iso2c")
# Merging
data_merged = left_join(borders, collapsed_flfp, by=c("iso2c"))
data_merged = st_sf(data_merged)

# Getting map of the world
worldmap = ne_countries(scale="large", returnclass="sf")

# Mapping the data
ggplot()+
  geom_sf(data=worldmap)+
  geom_sf(data=data_merged, aes(fill=average))+
  scale_fill_viridis(option="viridis")
```
Based on the above map, regions in Southern Africa have high amounts of female participation in the workforce. 

```{r}
# Mapping Africa
africamap = ne_countries(continent="africa", scale="large", returnclass="sf")
africadata = subset(data_merged, iso2c %in% africamap$iso_a2)
ggplot()+
  geom_sf(data=africamap)+
  geom_sf(data=africadata, aes(fill=average))+
  scale_fill_viridis(option="viridis")+
  theme_void()

```

9. A Shiny app involves 1) a user-interface (UI), 2) a server, and 3) executing the Shiny app. Within the UI, you must specify both Inputs and Outputs. Within the server, you store directions in objects and use render functions to output what's stored in those objects. And when you execute the Shiny App, you specify the names of your UI an dserver. 

```{r}
# Loading and preparing PDF
library(pdftools)
library(tidytext)
library(stringr)
data(stop_words)
USAID = pdf_text("PA00TNMJ.pdf")
armeniatext = as.data.frame(USAID, stringAsFactors=FALSE)
armeniatext$page = c(1:59)
colnames(armeniatext)[which(names(armeniatext)=="USAID")] = "text"
# Tokenize and remove stop words
tidyarmenia = armeniatext%>%
  unnest_tokens(word, text)%>%
  anti_join(stop_words)
# Word counts
armenia_count = tidyarmenia%>%
  count(word, sort=TRUE)%>%
  top_n(5, n)
armenia_count
# The top five words are LAW, CORRUPTION, RULE, ARMENIA, and EUROPEAN
```

```{r}
library(rvest)
library(dplyr)
library(ggplot2)
library(xml2)
# Loading webpage
hot100exam = "https://www.billboard.com/charts/hot-100"
hot100exam = read_html(hot100exam)
# Getting nodes
hot100nodes = hot100exam%>%
  html_nodes("body")%>%
  html_children()
hot100nodes

# Pulling data on RANK, ARTIST, TITLE, and LAST WEEK
rank = hot100exam %>%
  rvest::html_nodes("body")%>%
  xml2::xml_find_all("//span[contains(@class,
                     'chart-element__rank__number')]")%>%
  rvest::html_text()

artist = hot100exam %>%
  rvest::html_nodes("body")%>%
  xml2::xml_find_all("//span[contains(@class,
                     'chart-element__information__artist')]")%>%
  rvest::html_text()

title = hot100exam %>%
  rvest::html_nodes("body")%>%
  xml2::xml_find_all("//span[contains(@class,
                     'chart-element__information__song')]")%>%
  rvest::html_text()

lastweek= hot100exam%>%
  html_nodes("body")%>%
  xml_find_all("//span[contains(@class, 'chart-element__meta text--center color--secondary text--last')]")%>%
  html_text()

hot100df = data.frame(rank, artist, title, lastweek)
```


```{r}
library(rio)
export(collapsed_flfp, "collapsed_flfp.dta")
```

